Nail: A practical interface generator for data formats

### 2015-08-10 paper/thesis/abstract.tex
thesis

% $Log: abstract.tex,v $
% Revision 1.1  93/05/14  14:56:25  starflt
% Initial revision
% 
% Revision 1.1  90/05/04  10:41:01  lwvanels
% Initial revision
% 
%
%% The text of your abstract and nothing else (other than comments) goes here.
%% It will be single-spaced and the rest of the text that is supposed to go on
%% the abstract page will be generated by the abstractpage environment.  This
%% file should be \input (not \include 'd) from cover.tex.
In this thesis, I designed and implemented a compiler which performs
optimizations that reduce the number of low-level floating point operations
necessary for a specific task; this involves the optimization of chains of
floating point operations as well as the implementation of a ``fixed'' point
data type that allows some floating point operations to simulated with integer
arithmetic.  The source language of the compiler is a subset of C, and the
destination language is assembly language for a micro-floating point CPU.  An
instruction-level simulator of the CPU was written to allow testing of the
code.  A series of test pieces of codes was compiled, both with and without
optimization, to determine how effective these optimizations were.

>>>>

% $Log: abstract.tex,v $
% Revision 1.1  93/05/14  14:56:25  starflt
% Initial revision
% 
% Revision 1.1  90/05/04  10:41:01  lwvanels
% Initial revision
% 
%
%% The text of your abstract and nothing else (other than comments) goes here.
%% It will be single-spaced and the rest of the text that is supposed to go on
%% the abstract page will be generated by the abstractpage environment.  This
%% file should be \input (not \include 'd) from cover.tex.

\textit{Nail} is a tool that greatly reduces the
programmer effort for safely parsing and generating data formats defined
by a grammar.
Nail introduces several key
ideas to achieve its goal.  First, Nail uses a protocol grammar to
define not just the data format, but also the internal object model
of the data.  Second, Nail eliminates the notion of semantic actions,
used by existing parser generators, which reduces the expressive power
but allows Nail to both {\em parse} data formats and {\em generate}
them from the internal object model, by establishing a {\em semantic
bijection} between the data format and the object model.  Third,
Nail introduces {\em dependent fields} and {\em stream transforms} to
capture protocol features such as size and offset fields, checksums,
and compressed data, which are impractical to express in existing
protocol languages.  Using Nail, we implement an authoritative  DNS server in
C in under 300 lines of code and grammar, and an {\tt unzip}
program in C in 220 lines of code and grammar, demonstrating that Nail
makes it easy to parse complex real-world data formats.  Performance
experiments show that a Nail-based DNS server can outperform the widely
used BIND DNS server on an authoritative workload,
 demonstrating that systems built with Nail can achieve good
performance.
